% !TEX TS-program = pdflatexmk

\documentclass[10pt,sigconf,letterpaper]{acmart}

\usepackage{xspace}
\usepackage{enumitem}
\usepackage{footmisc}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{colortbl} % coloring in tables
\usepackage{soul}

% TODO change to anrw style

%\setcopyright{acmlicensed}
%\copyrightyear{2025}
%\acmYear{2025}
%\acmDOI{XXXXXXX.XXXXXXX} % TODO

\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
\setcopyright{none}
\settopmatter{printacmref=false, printccs=false, printfolios=true}
 
 \begin{document}
 \pagestyle{plain}
 \pagenumbering{arabic}
  
 \title{Tracing Anycast: a Performance Assessment}

 \newif\ifisanon

\iftrue
\newcommand{\raf}[1]{\textcolor{violet}{\noindent[Raf: #1]}}
\else
\newcommand{\raf}[1]{}
\fi
 
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\etc}{\textit{etc.}}
\newcommand{\eg}{\textit{e.g.}}
 
%flip  here to disable anonymization in the paper
%\isanonfalse
\isanontrue

\ifisanon

\author{Paper \#A, B pages body, C pages total}
\else 
\author{blaat
}

\fi

\def \manycasttwo  {MAnycast\textsuperscript{2}\xspace}
\def \manycast  {MAnycastR\xspace}

\begin{abstract}
Anycast allows for providing services from multiple, geographically distant, Points of Presence (PoPs) using a single IP address to \eg, provide increased resilience.
However, due to its opaqueness it is often unknown which addresses are provided using anycast and, if so, where its PoPs are located.
As anycast is widely used for \eg, critical Internet infrastructure like the DNS, there have been efforts in mapping anycast deployments.
The current state-of-the-art, a technique called iGreedy, relies on latency measurements. % to detect anycast and allows for geolocating PoPs using trilateration similar to conventional unicast IP geolocation.
However, such measurements are noisy as they suffer from \eg, network propagation delays.

Previous work has shown that traceroute, a technique that reveals the individual hops a packet traverses, can be used to detect anycast. % as distinct PoPs will have different neighboring routers.
Furthermore, it can locate anycast using available geolocation data of hops near anycast PoPs. 

This work is the first to assess the performance of the traceroute technique at scale by performing it towards O(4) anycast prefixes.
Our results show ...
We provide an extensive validation of the traceroute technique, publicly release our code, and release an extensive geolocation dataset of anycast networks.

\end{abstract}

\maketitle

\input{introduction.tex}

\input{background.tex}

\input{methodology.tex}

\input{results.tex}

\input{discussion.tex}

\section{Acknowledgements}
kc would like us to acknowledge the GMI grant.

\bibliographystyle{ACM-Reference-Format}
\bibliography{atr}

%\appendix

%\input{appendix.tex}

\end{document}
\endinput

