- Introduction
    - Goal: Analysis of parental control technologies in routers and software solutions.
    - Research questions:
        - How do different parental control solutions implement inappropriate/malicious website blocking?
        - How do they compare in terms of effectiveness?
- Background and related work:
    - What are parental controls?
    - Why are they used?
    - What mechanisms do they use? (DNS, blacklists, interception...)
    - Previous studies on effectiveness and circumvention
    - Comparison to censorship research (?)
- Methodology:
    - What did we decide to do?
    - How did we chose the routers and softwares?
    - TP Link use case
    - How did we obtain the lists?
        - Overview of list we used
        - Classification and re-classification
    - Data Capturing
        - Environment
        - Tests
        - Router behaviour
        - Software behaviour
        - Blocked domain recognition and extraction
- Datasets (importante per TMA)
    - Descrizioni accurate quando, cosa, data points
    - Analysis of each list we used
- Results
    - Overview of the software used to analyze the Results (forse Methodology)
    - Results obtained 
    - Baseline
    - Comparison between each router, each software, different levels on routers, and between both router and software
    - Key findings:
        - How effective are these tools at blocking content?
- Limitations and future work:
    - Longitudinal study of changes in filtering policies.
    - Testing with different classificated lists.
- Conclusion