%\documentclass{article} % Or some other class?  like 'report' or 'IEEEtran'
\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}  
\usepackage{graphicx}        
\usepackage{cite} 
\usepackage{amsmath, amssymb}
\usepackage{hyperref}        
%\usepackage{natbib}       
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{booktabs}
\usepackage{soul}        
\usepackage{svg}
\usepackage{hyperref}  
\usepackage{cleveref}

\newcommand\Mycite[1]{%             
  \citeauthor{#1}~\cite{#1}} 
% Produce citation in style     John et al. [1]         using \Mycite{}
% for citations in style        John et al. [2020]      change line 16 to    \citeauthor{#1}~[\citeyear{#1}]} 
  
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
    
\begin{document}

\title{To Block Or Not To Block? Evaluating Parental Controls Across Routers, DNS Services, and Software}


\author{\IEEEauthorblockN{Matteo Liberato}
\IEEEauthorblockA{University of Twente\\
m.liberato@utwente.nl}}

\author{\IEEEauthorblockN{Antonia Affinito}
\IEEEauthorblockA{University of Twente\\
a.affinito@utwente.nl}}

\author{\IEEEauthorblockN{Bernd Meijerink}
\IEEEauthorblockA{University of Twente\\
bernd.meijerink@utwente.nl}}

\author{\IEEEauthorblockN{Ralph Holz}
\IEEEauthorblockA{University of M\"{u}nster\\
ralph.holz@uni-muenster.del}}

\author{\IEEEauthorblockN{Mattijs Jonker}
\IEEEauthorblockA{University of Twente\\
m.jonker@utwente.nl}}

\author{\IEEEauthorblockN{Alessio Botta}
\IEEEauthorblockA{Universit\`{a} degli Studi di Napoli Federico II\\
a.botta@unina.it}}

\author{\IEEEauthorblockN{Anna Sperotto}
\IEEEauthorblockA{University of Twente\\
a.sperotto@utwente.nl}}


\author{\IEEEauthorblockN{Anonymous Authors}}


\maketitle

\begin{abstract}
In today's society, ensuring the safety of children online has become a priority for parents, educators, and policymakers. Parental control systems are widely used to restrict access to age-inappropriate online content, offering a tool for protecting children from potential online risks.
However, their blocking behavior across different technologies remains hidden and poorly analyzed.
In this paper, we present a comparative analysis of seven parental control solutions: three provided by routers with built-in filtering functionalities (TP-Link, Netgear, and ASUS), two DNS-based services (OpenDNS and DNS.eu), and a software tool (Norton Family).
Each system was tested by systematically visiting a large set of domains and recording which were blocked.
We then classified all domains into content categories and used this classification to evaluate the consistency and selectivity of each parental control system.
Our findings show that parental controls frequently fall short of providing adequate protection: Some systems fail to block up to 96\% of inappropriate domains, while others block appropriate content or apply inconsistent and arbitrary filtering rules.
For example, ASUS allows access to over 95\% of gambling websites, and Netgear exhibits internal inconsistencies, with one-third of the domains blocked under its "Adult" settings remaining accessible under its stricter "Child" setting.
These results provide insight into the real-world operation of popular parental control technologies and show a methodology for evaluating category-based filtering at scale.
\end{abstract}

\begin{IEEEkeywords}
Network measurements, Use and digitalization, Parental control.
\end{IEEEkeywords}

% Each parts automatically adds .tex to the input field

\section{Introduction}
\input{1_Introduction}  

\section{Background \& Related work}\label{sec:rw}
\input{2_Background_and_related_work_Antonia}  

\section{Methodology}\label{sec:methodology}
\input{3_Methodology}  

\section{Dataset}\label{sec:dataset}
\input{4_Dataset}

\section{Results}\label{sec:results}
\input{5_Results} 

\section{Discussion}\label{sec:discussion}
\input{6_Limitations_and_future_works}

\section{Conclusions}\label{sec:conclusions}
\input{7_Conclusion} 

%TODO: DO NOT FORGET ACKS
%\textbf{Acknowledgements --} CVD, Cisco 

\bibliographystyle{IEEEtran} 
\bibliography{references}  % references go in references.bib

\appendix

\subsection{Ethical Considerations}
Our measurement approach involves active measurements, both at the DNS level
(routers and DNS services) and the HTTPS level (software). We took care to
avoid undue load on the on the infrastructure of the services we were testing.
For the routers, we performed fewer than 120 DNS $requests/s$, which is
well below the number of requests a resolver is able to handle in operational
settings.
For the DNS service, taking into account that they involve open resolvers
dedicated not only to parental control functionality, we set an even more cautious
pace, limiting ourselves to 300K $requests/day$ (3.5 $requests/sec$).
Finally, the software solutions appeared not to directly rely on a back-end
infrastructure, so we did not apply any explicit pacing as the measurement is
naturally quite slow. To further limit any possible impact, we focused on a
one-shot measurement.
For website categorization we rely on data provided by Cisco. A number of
Top sites contain potentially disturbing content. During the
measurements we took care that we never visually load any of those pages. 

\end{document}
